---
title: "Homework 01"
---


## TidyTuesday Part

```{r}
library(tidyverse)
tuesdata <- tidytuesdayR::tt_load('2026-09-08')

cafe <- tuesdata$cafe
cappuccino_index <- tuesdata$cappuccino_index
```
# Research Question:

How does cappuccino affordability vary by country?


```{r}
cappuccino_clean <- cappuccino_index |>
  mutate(
    country = str_replace_all(country, "\u00a0", " ")
  )
```

```{r}
most_affordable <- cappuccino_clean |>
  slice_min(order_by = index, n = 5)

least_affordable <- cappuccino_clean |>
  slice_max(order_by = index, n = 5)

most_affordable
least_affordable
```


```{r}
extreme_countries <- bind_rows(
  most_affordable |>
    mutate(group = "Most affordable"),
  
  least_affordable |>
    mutate(group = "Least affordable")
)
```

```{r}
ggplot(extreme_countries, aes(x = index, y = fct_reorder(country, index),
    fill = group)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = paste0(round(index, 1), " min")), hjust = -0.1, size = 3.5,
    ) +
  facet_wrap(vars(group), scales = "free_y", ncol = 1
  ) +
  scale_fill_manual(
    values = c(
      "Most affordable" = "green",
      "Least affordable" = "red"
    )
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0, 0.15))
  ) +
  labs(
    title = "Where is a cappuccino most and least affordable?",
    subtitle = "In minutes of barista work",
    x = "Minutes of work",
    y = NULL,
    caption = "Source: TidyTuesday"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_blank(),
    
  )
```

This plot tells us that Pakistan, Qatar, Djibouti, India and Vietnam's barista workers have to spend the most working time to afford a cappuccino, while the Netherlands, Switzerland, New Zealand, Italy and Australia's barista workers can spend the least working time to afford a cappuccino. On average, Australia's barista workers work for the shortest time, 10.1 minutes, to afford a cappuccino, while Pakistan's barista workers work for the longest time, 277 minutes, to afford a cappuccino.

However, this data may not be entirely accurate, because the size of the sample for each countries vary a lot.

```{r}
plot_data <- cappuccino_clean |>
  filter(n > 15) |>
  mutate(
    country = fct_reorder(country, index, .desc = TRUE)
  ) |>
  select(country, index, n) |>
  pivot_longer(
    cols = c(index, n),
    names_to = "measure",
    values_to = "value"
  ) |>
  mutate(
    measure = recode(
      measure,
      index = "Minutes of work",
      n = "Sample size"
    )
  )
```

```{r}
ggplot(
  cappuccino_clean |>
    filter(n > 10) |>
    mutate(country = fct_reorder(country, index, .desc = TRUE)),
  aes(x = index, y = country)
) +
  geom_col(width = 0.75, fill = "#614425") +
  labs(
    title = "A small cappuccino: minutes of barista work needed by country",
    subtitle = "In India, it takes about 8 times as many minutes of work as in Australia.",
    x = "Minutes of work",
    y = NULL,
    caption = "Author: Jason You | Source: Cappuccino Index, TidyTuesday")+
  theme_minimal() +
  theme(panel.grid.major.y = element_blank())
```
This plot tells us about average minutes of work a barista have to spend to afford a cup of cappuccino by country. However, this data is distorted by the sample size of the dataset. The bar graph of the right shows how large each country's sample is. 
