---
title: "Homework 01"
---


## TidyTuesday Part

```{r}
library(tidyverse)
tuesdata <- tidytuesdayR::tt_load('2026-09-08')

cafe <- tuesdata$cafe
cappuccino_index <- tuesdata$cappuccino_index
```
# Research Question:

How does cappuccino affordability vary by country?


```{r}
cappuccino_clean <- cappuccino_index |>
  mutate(
    country = str_replace_all(country, "\u00a0", " ")
  )
```

```{r}
most_affordable <- cappuccino_clean |>
  slice_min(
    order_by = index,
    n = 5,
    with_ties = FALSE
  )

least_affordable <- cappuccino_clean |>
  slice_max(
    order_by = index,
    n = 5,
    with_ties = FALSE
  )

most_affordable
least_affordable
```


```{r}
extreme_countries <- bind_rows(
  most_affordable |>
    mutate(group = "Most affordable"),
  
  least_affordable |>
    mutate(group = "Least affordable")
)
```

```{r}
ggplot(extreme_countries, aes(x = index, y = fct_reorder(country, index),
    fill = group)) +
  geom_col(width = 0.7) +
  geom_text(
    aes(label = paste0(round(index, 1), " min")), hjust = -0.1, size = 3.5) +
  facet_wrap(vars(group), scales = "free_y", ncol = 1
  ) +
  scale_fill_manual(
    values = c(
      "Most affordable" = "green",
      "Least affordable" = "red"
    )
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0, 0.15))
  ) +
  labs(
    title = "Where is a cappuccino most and least affordable?",
    subtitle = "In minutes of barista work",
    x = "Minutes of work",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_blank()
  )
```

This plot tells us that Pakistan, Qatar, Djibouti, India and Vietnam's barista workers have to spend the most working time to afford a cappuccino, while the Netherlands, Switzerland, New Zealand, Italy and Australia's barista workers can spend the least working time to afford a cappuccino. On average, Australia's barista workers work for the shortest time, 10.1 minutes, to afford a cappuccino, while Pakistan's barista workers work for the longest time, 277 minutes, to afford a cappuccino.

```{r}
plot_data <- cappuccino_clean |>
  mutate(
    country = fct_reorder(country, index, .desc = TRUE)
  ) |>
  select(country, index, n) |>
  pivot_longer(
    cols = c(index, n),
    names_to = "measure",
    values_to = "value"
  ) |>
  mutate(
    measure = recode(
      measure,
      index = "Minutes of work",
      n = "Sample size"
    )
  )
```

```{r}
ggplot(
  plot_data,
  aes(x = value, y = country, fill = measure)) +
  geom_col(width = 0.75) +
  facet_grid(cols = vars(measure)) +
  scale_fill_manual(
    values = c(
      "Minutes of work" = "#614425",
      "Sample size" = "darkblue"
    )) +
  labs(
    title = "Cappuccino affordability and sample size by country",
    x = NULL,
    y = NULL,
    fill = NULL,
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    panel.grid.major.y = element_blank())
```
This plot tells us about average minutes of work a barista have to spend to afford a cup of cappuccino by country. However, this data is distorted by the sample size of the dataset. The bar graph of the right shows how large each country's sample is. 
