---
title: "Homework 02"
---


## TidyTuesday Part (Optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work.

:::

Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story mainly composed of [effective visualizations](https://docs.google.com/presentation/d/1WHr6Itzm2IJLxvppcacxHpr8R4NxO4MfvWWUPmtQx6Q/preview?slide=id.g13360dab5d5_0_61).  Provide sufficient background for readers to grasp your narrative.  Refer to the Homework Instructions ⭐ page on the course website for details on how to submit this part.

```{r}
library(tidyverse)
tuesdata <- tidytuesdayR::tt_load('2026-09-15')
## OR
tuesdata <- tidytuesdayR::tt_load(2026, week = 37)

dead_sea_scrolls <- tuesdata$dead_sea_scrolls

head(dead_sea_scrolls)
```

> Research question: Which are the most common compositions among the dead sea scrolls, and where are they distributed?

```{r}
top_compositions <- dead_sea_scrolls |>
  filter(composition != "Unidentified") |>
  count(composition, sort = TRUE) |>
  slice_head(n = 15)

ggplot(
  top_compositions,
  aes(x = n, y = fct_reorder(composition, n))
) +
  geom_col(fill = "#8C5A3F", width = 0.75) +
  geom_text(
    aes(label = n),
    hjust = -0.2,
    size = 3.5
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0, 0.12))
  ) +
  labs(
    title = "Which works appear most frequently among the Dead Sea Scrolls?",
    x = "Number of manuscripts",
    y = NULL,
    caption = "Author: Jason You | Source: Leon Levy Dead Sea Scrolls Digital Library, Tidy Tuesday"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.y = element_blank()
  )
```
> This graph shows the top 15 most common compositions found in the dead sea. The most common compositions is Psalms, followed by Deuteronomy and Phylacteries. There are a lot of compositions with the same number of appearance at 12 and 9.

```{r}
top_names <- top_compositions |>
  slice_head(n = 12) |>
  pull(composition)

cave_compositions <- dead_sea_scrolls |>
  filter(site_parent == "Qumran", composition %in% top_names,!is.na(cave)) |>
  count(cave, composition)

ggplot(
  cave_compositions,
  aes(x = factor(cave), y = composition, fill = n)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(aes(label = n), size = 3) +
  scale_fill_gradient(low = "#F3E9D7", high = "#8C5A3F") +
  labs(
    title = "Distribution of compositions types across the caves",
    x = "Cave #",
    y = NULL,
    fill = "Manuscripts",
    caption = "Author: Jason You | Source: Leon Levy Dead Sea Scrolls Digital Library, Tidy Tuesday"
  ) +
  theme_minimal() +
  theme(
    panel.grid = element_blank()
  )
```

> This graph shows that cave 4 have the most amount of scrolls, with all of the types of compositions and the most amount of each of them, while Cave 6 have the least amount of scolls, only one Damascus Document.
