---
title: "Homework 03"
---


## TidyTuesday Part (Optional)

::: {.callout-important title="Instructions"}
You can count work on this week's TidyTuesday toward the exceptional work.
:::

Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story mainly composed of [effective visualizations](https://docs.google.com/presentation/d/1WHr6Itzm2IJLxvppcacxHpr8R4NxO4MfvWWUPmtQx6Q/preview?slide=id.g13360dab5d5_0_61).  Provide sufficient background for readers to grasp your narrative.  Refer to the Homework Instructions ⭐ page on the course website for details on how to submit this part.


```{r}
library(tidyverse)
library(ggplot2)
library(tidymodels)
library(ggforce)
tuesdata <- tidytuesdayR::tt_load(2026, week = 38)
urban <- tuesdata$urban
```



```{r}
china_cities <- urban |>
  filter(countryOrTerritoryName == "China", cityName %in% c("Beijing", "Hangzhou", "Chengdu"
                                                            , "Suzhou", "Qingdao", "Haikou",
                                                            "Tianjin"))
```

```{r}
ggplot(
  china_cities,
  aes(
    x = year,
    y = averageShareOfGreenAreaInCityUrbanAreaPct,
    color = cityName,
    group = cityName
  )
) +
  geom_line(linewidth = 1) +
  geom_point(size = 2.5) +
  scale_x_continuous(
    breaks = c(1990, 2000, 2010, 2020, 2025)
  ) +
  labs(
    title = "Share of urban area classified as green in China, 1990–2025",
    x = NULL,
    y = "Green area (%)",
    color = NULL,
    caption = "Author: Jason You | Source: TidyTuesday, UN-Habitat Urban Indicators Database, Sept, 22nd, 2026"
  ) +
  theme_minimal() +
  theme(
    legend.position = "top"
  )
```
```{r}
city_change <- china_cities |>
  filter(year %in% c(1990, 2020)) |>
  select(cityName, year, averageShareOfGreenAreaInCityUrbanAreaPct) |>
  pivot_wider(
    names_from = year,
    values_from = averageShareOfGreenAreaInCityUrbanAreaPct,
    names_prefix = "green_"
  ) |>
  mutate(change = green_2020 - green_1990)


ggplot(
  city_change,
  aes(
    y = fct_reorder(cityName, change),
    color = change > 0
  )
) +
  geom_segment(
    aes(
      x = green_1990,
      xend = green_2020,
      yend = cityName
    ),
    linewidth = 1,
    arrow = arrow(type = "open", length = unit(0.1, "inches"))
  ) +
  scale_color_manual(
    values = c(
      "TRUE" = "darkgreen",
      "FALSE" = "red"
    ),
    guide = "none"
  ) +
  scale_x_continuous(
    labels = scales::label_percent(scale = 1)
  ) +
  labs(
    title = "Change in Chinese Cities' Green-Area Share from 1990 to 2020",
    subtitle = "Beijing is the only city that became greener",
    x = NULL,
    y = NULL,
    caption = "Author: Jason You | Source: TidyTuesday, UN-Habitat Urban Indicators Database, September 22, 2026"
  ) +
  theme_minimal() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    plot.caption = element_text(hjust = 0)
  )
```

